---
title: "notes-05-03-20"
author: "Austin Meyer"
date: "3/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("ggplot2")
library("plotly")
```

# Read in data set

```{r}
df <- read.csv("https://raw.githubusercontent.com/roualdes/data/master/droughts.csv")

head(df)
```

* Discreate: Can take on only a specific amount of values (counting values)
* Continuous: Can take on any value as it goes past infinity

This will pull out the column with the name that is after ($)
```{r}
head(df$length)

class(df$length)
class(df)
```

We can estimate lamda as:
```{r}
1 / mean(df$length)
```

This means it will rain one day out of two days. Another way to state this is one rain event every two days.

```{r}
mean(df$length)
```

The expression above would be said: Every 2 days it will rain.

## Fancy Plot

```{r}
x_plot <- ggplot(df, aes(x = length)) + geom_histogram(bins = 40)
ggplot(df, aes(x = year)) + geom_histogram(bins = 21)
# ggplotly(x_plot)
```

# Exponential

There is a named function in r for randomly sampling for exponential.
```{r}
?rexp
```

# Normal Distribution

```{r}
x <- rnorm(1001)
head(x)

df <- data.frame(x = x)

x_plot <- ggplot(df, aes(x)) + geom_density()
```

How many observations exist in between -2 and 2

```{r}
mean(x > -2 && x < 2)
```

Now add a function too our graph

```{r}
x_plot + stat_function(fun = dnorm, color = "orange")
```

